The Effect of Elections and Changed Governments on Discussion in the Australian Federal Parliament (1901--2017)

### 2018-11-21 outputs/docs/events/paper.Rmd
Update footnotes and appendix with errors list

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Elections and Changed Governments on Discussion in the Australian Federal Parliament (1901--2017)"
thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. We are grateful for the many excellent comments that we received from seminar participants at the ANU School of Politics and International Relations, the ANU Research School of Economics, and the Parliamentary Library. Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how discussion in the Australian Federal Parliament changes in response to elections and changed governments. We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records. To reduce the dimensionality of this dataset we use a correlated topic model, and then analyse the effect of various events using a Bayesian hierarchical Dirichlet model. We find that: changes in government tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in government are rarely associated with topic changes. The effect of events is much more pronounced in the second half of our sample, and especially in the past two decades. This has implications for how we think about the longer-term trajectory of government policymaking as the media and political cycles becomes increasingly focused on short-term events."
keywords: "text-as-data, Australian political history, unsupervised machine learning, Bayesian hierarchical Dirichlet model"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

The key assumption behind LDA is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then choose words, 'terms', that are appropriate to those topics. A topic could be thought of as a collection of terms, and a document as a collection of topics, where these collections are defined by probability distributions. The topics are not specified *ex ante*; they are an outcome of the method, and it is in this sense that this approach can be considered unsupervised machine learning. Terms are not necessarily unique to a particular topic, and a document could be about more than one topic. The goal is to have the words found in each day's Hansard group themselves to define topics. This can provide more flexibility than other approaches such as a strict word count method, but can require a larger dataset and make interpretation more difficult. A

An overview and simplified example of how topic modelling works is available in Appendix \@ref(LDAoverviewandexample). The underlying document generation process is discussed in Appendix \@ref(LDAdocgenprocess), and Appendix \@ref(LDAposteriorestimation) explains how this is reversed to generate topics. Finally, the choice of the number of topics has a large effect on the composition of the topics, and some diagnostics for selecting the appropriate number are discussed in Appendix \@ref(selecttopicnumber).

@@

top_words %>% 
  kable(booktabs = T, longtable = TRUE, caption = "Top words associated with each topic") %>%
  kable_styling(font_size = 8, latex_options = c("repeat_header"))

@@

governments_results %>%
  kable(booktabs = T, caption = "Governments that were significantly different to their predecessor") %>%
  kable_styling(font_size = 10)

@@

elections_results %>%
  kable(booktabs = T, caption = "Elections that were significantly different to the one before") %>%
  kable_styling(font_size = 10) %>% 
  footnote(general = "Here is a general comments of the table. ")

@@

key_events_results_cols %>%
  kable(booktabs = T, caption = "Days that were significantly different to other days in their sitting period") %>%
  kable_styling(font_size = 10)

@@

## Compared with parliamentary website {#knownhansardissues}
The parliamentary website provides a summary table of the number of sitting days in each year by chamber.[^parliamentarywebsitelink] Comparing the numbers provided in that table with number of days that we have provides an indication of how complete our dataset is.

@@

The two major years of concern are 1992 in the House of Representatives where we have 15 days more than the parliamentary website claims there were, and 1988 in the Senate where we have eight days fewer.

The Parliament website is missing the Hansard PDFs for the following dates in the Senate: 
1988-12-21, 1988-12-20, 1988-12-19, 1988-12-16, 1988-12-15, 1988-12-14, 1988-12-13, 1988-12-12, 2000-10-12, 2000-06-19, 2004-08-09.

@@

The Parliament website is missing the Hansard PDFs for the following dates in the House of Representatives: 
1985-08-23,
1992-09-10,
1996-12-13,
2002-05-14,
2000-10-12, and
2000-06-29.

@@

In the Senate, the PDF for 10 August 1917 may be the wrong one. It says it is for 10 January 1918 on the cover sheet, but there's not an entry for 10 January 1918.

Senate Hansard - 1918-12-18 has the wrong PDF so does 1917-08-01.

>>>>

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Elections and Changed Governments on Discussion in the Australian Federal Parliament (1901--2017)"
thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. We are grateful for the many excellent comments that we received from seminar participants at the ANU School of Politics and International Relations, the ANU Research School of Economics, and the Parliamentary Library. Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how discussion in the Australian Federal Parliament changes in response to elections and changed governments. We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records. To reduce the dimensionality of this dataset we use a correlated topic model, and then analyse the effect of various events using a Bayesian hierarchical Dirichlet model. We find that: changes in government tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in government are rarely associated with topic changes. The effect of events is much more pronounced in the second half of our sample, and especially in the past two decades. This has implications for how we think about the longer-term trajectory of government policymaking as the media and political cycles becomes increasingly focused on short-term events."
keywords: "text-as-data, Australian political history, unsupervised machine learning, Bayesian hierarchical Dirichlet model"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no

header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}

---

@@

The key assumption behind LDA is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then choose words, 'terms', that are appropriate to those topics. A topic could be thought of as a collection of terms, and a document as a collection of topics, where these collections are defined by probability distributions. The topics are not specified *ex ante*; they are an outcome of the method, and it is in this sense that this approach can be considered unsupervised machine learning. Terms are not necessarily unique to a particular topic, and a document could be about more than one topic. The goal is to have the words found in each day's Hansard group themselves to define topics. This can provide more flexibility than other approaches such as a strict word count method, but can require a larger dataset and make interpretation more difficult.

An overview, and an example, of how topic modelling works is available in Appendix \@ref(LDAoverviewandexample). The underlying document generation process is discussed in Appendix \@ref(LDAdocgenprocess), and then Appendix \@ref(LDAposteriorestimation) explains how this is reversed to generate topics. Finally, Appendix \@ref(selecttopicnumber) contains a discussion of how the number of topics was chosen.

@@

top_words %>% 
  kable("latex", booktabs = T, longtable = TRUE, caption = "Top words associated with each topic") %>%
  kable_styling(font_size = 8, latex_options = c("repeat_header")) %>% 
  footnote(general = "We display only the top ten words for each topic, but the topics are defined by probability distributions over all words.")

@@

governments_results %>%
  kable(booktabs = T, caption = "Governments that were significantly different to their predecessor") %>%
  kable_styling(font_size = 10) %>% 
  footnote(
    general = "The significance of a government is determined by whether at least one topic was significantly different during this government, compared with the previous one.", 
    footnote_as_chunk = T, 
    threeparttable = TRUE)

@@

elections_results %>%
  kable(booktabs = T, caption = "Election-periods that were significantly different to the one before") %>%
  kable_styling(font_size = 10) %>% 
   footnote(
    general = "The significance of a government is determined by whether at least one topic was significantly different during the period between this election and the next, compared with the previous one.", 
    footnote_as_chunk = T, 
    threeparttable = TRUE)

@@

key_events_results_cols %>%
  kable(booktabs = T, caption = "Days that were significantly different to other days in their sitting period") %>%
  kable_styling(font_size = 10) %>% 
  footnote(
    general = "These days were significantly different to others in their sitting period after taking election and government effects into consideration.", 
    footnote_as_chunk = T, 
    threeparttable = TRUE)

@@

## Annual counts of sitting days, compared with parliamentary website {#knownhansardissues}
The parliamentary website provides a summary table of the number of sitting days in each year by chamber.[^parliamentarywebsitelink] Comparing the numbers provided in that table with number of days that we have provides an indication of how complete our dataset is.

@@

The two major years of concern are 1992 in the House of Representatives where we have 15 days more than the parliamentary website claims there were, and 1988 in the Senate where we have eight days fewer. We examined the physical copy of the Hansard kept in the NSW State Library and this suggests that the summary table on the parliamentary website may be wrong.

The Parliament website is missing the Hansard PDFs for the following dates in the Senate: 
1988-12-21, 
1988-12-20, 
1988-12-19, 
1988-12-16, 
1988-12-15, 
1988-12-14, 
1988-12-13, 
1988-12-12, 
2000-10-12, 
2000-06-19, and
2004-08-09.

@@

The Parliament website is missing the Hansard PDFs for the following dates in the House of Representatives: 
1985-08-23,
1992-09-10,
1996-12-13,
2000-10-12,
2000-06-29, and 
2002-05-14.

@@

In terms of other issues, in the Senate, the PDF for 10 August 1917 may be the wrong one. It says that it is for 10 January 1918 on the cover sheet, but there's no an entry for 10 January 1918. Similarly for 1918-12-18 and 1917-08-01.
